---
title: "Boston Housing"
author: "João Pedro Schmitt"
date: "27 de novembro de 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

Final project developed to get grade in the coursera class of Developing Data Products. This project was made using the **slidify** and **shiny** to build the presentation and analysis.

- Available at: [https://schmittjoaopedro.shinyapps.io/final_project/](https://schmittjoaopedro.shinyapps.io/final_project/)
- Comparable tab: relationship between the choose variable and the median value of home-occupied by 1000 USD.
- Prediction tab: a table with the best fitted linear model and input fields to predict a median value.
- Dataset tab: used data to build the project.

## Data

Data analisys for housing data for 506 census tracts of Boston from the 1970 census. The dataframe BostonHousing contains the original data by Harrison and Rubinfeld (1979).

Variables:

- **crim** = per capita crime rate by town
- **zn** = proportion of residential land zoned for lots over 25,000 sq.ft
- **indus** = proportion of non-retail business acres per town
- **chas** = Charles River dummy variable (= 1 if tract bounds river; 0 otherwise)
- **nox** = nitric oxides concentration (parts per 10 million)

***

- **rm** = average number of rooms per dwelling
- **age** = proportion of owner-occupied units built prior to 1940
- **dis** = weighted distances to five Boston employment centres
- **rad** = index of accessibility to radial highways
- **tax** = full-value property-tax rate per USD 10,000
- **ptratio** = pupil-teacher ratio by town
- **b** = 1000(B - 0.63)^2 where B is the proportion of blacks by town
- **lstat** = percentage of lower status of the population
- **medv** = median value of owner-occupied homes in USD 1000's

## Loading the dataset

```{r echo=TRUE}
library(mlbench)
data(BostonHousing)
head(BostonHousing)
```